Residence time, a master variable of ecology, physiology, and natural selection

### 2015-09-12 analyses/ForPaper/PrimaryPredictions.Rmd

f.dat <- subset(dat, motion == "fluid")
r.dat <- subset(dat, motion == "random_walk")
```

@@

  stat_smooth(aes(x=dat$h.tau, y=dat$total.abundance, group=dat$motion, colour=dat$motion),
    data=dat, method = "lm", geom="smooth", linetype="dashed", size=1,
    formula = y ~ poly(x,2), se=FALSE) +

  scale_colour_manual(values = c("navy", "darkgreen"),
      labels = c(paste("Fluid, r^2 = ",round(f.N.2.r2,2)),
      paste("Non-fluid, r^2 = ",round(r.N.2.r2,2))),
      name = "") +

@@

  stat_smooth(aes(x=dat$h.tau, y=dat$species.richness, group=dat$motion, colour=dat$motion),
    data=dat, method = "lm", geom="smooth", linetype="dashed", size=1,
    formula = y ~ poly(x,2), se=FALSE) +

  scale_colour_manual(values = c("navy", "darkgreen"),
      labels = c(paste("Fluid, r^2 = ",round(f.S.2.r2,2)),
      paste("Non-fluid, r^2 = ",round(r.S.2.r2,2))),
      name = "") +

@@

  stat_smooth(aes(x=dat$h.tau, y=dat$e.var, group=dat$motion, colour=dat$motion),
    data=dat, method = "lm", geom="smooth", linetype="dashed", size=1,
    formula = y ~ poly(x,2), se=FALSE) +

  scale_colour_manual(values = c("navy", "darkgreen"),
      labels = c(paste("Fluid, r^2 = ",round(f.ev.2.r2,2)),
      paste("Non-fluid, r^2 = ",round(r.ev.2.r2,2))),
      name = "") +

@@

  stat_smooth(aes(x=dat$h.tau, y=dat$species.turnover, group=dat$motion, colour=dat$motion),
    data=dat, method = "lm", geom="smooth", linetype="dashed", size=1,
    formula = y ~ poly(x,2), se=FALSE) +

  scale_colour_manual(values = c("navy", "darkgreen"),
      labels = c(paste("Fluid, r^2 = ",round(f.to.2.r2,2)),
      paste("Non-fluid, r^2 = ",round(r.to.2.r2,2))),
      name = "") +

>>>>

f.dat <- subset(dat, motion == " fluid")
r.dat <- subset(dat, motion == " random_walk")
```

@@

  stat_smooth(aes(x=dat$h.tau, y=dat$total.abundance, group=dat$motion, colour=dat$motion),
    data=dat, method = "lm", geom="smooth", linetype="dashed", size=1,
    formula = y ~ poly(x,3), se=FALSE) +

  scale_colour_manual(values = c("navy", "darkgreen"),
      labels = c(paste("Fluid, r^2 = ",round(f.N.3.r2,2)),
      paste("Non-fluid, r^2 = ",round(r.N.3.r2,2))),
      name = "") +

@@

  stat_smooth(aes(x=dat$h.tau, y=dat$species.richness, group=dat$motion, colour=dat$motion),
    data=dat, method = "lm", geom="smooth", linetype="dashed", size=1,
    formula = y ~ poly(x,3), se=FALSE) +

  scale_colour_manual(values = c("navy", "darkgreen"),
      labels = c(paste("Fluid, r^2 = ",round(f.S.3.r2,2)),
      paste("Non-fluid, r^2 = ",round(r.S.3.r2,2))),
      name = "") +

@@

  stat_smooth(aes(x=dat$h.tau, y=dat$e.var, group=dat$motion, colour=dat$motion),
    data=dat, method = "lm", geom="smooth", linetype="dashed", size=1,
    formula = y ~ poly(x,3), se=FALSE) +

  scale_colour_manual(values = c("navy", "darkgreen"),
      labels = c(paste("Fluid, r^2 = ",round(f.ev.3.r2,2)),
      paste("Non-fluid, r^2 = ",round(r.ev.3.r2,2))),
      name = "") +

@@

  stat_smooth(aes(x=dat$h.tau, y=dat$species.turnover, group=dat$motion, colour=dat$motion),
    data=dat, method = "lm", geom="smooth", linetype="dashed", size=1,
    formula = y ~ poly(x,3), se=FALSE) +

  scale_colour_manual(values = c("navy", "darkgreen"),
      labels = c(paste("Fluid, r^2 = ",round(f.to.3.r2,2)),
      paste("Non-fluid, r^2 = ",round(r.to.3.r2,2))),
      name = "") +
